---
title: "Intermediate R"
author: "MAJ Dusty Turner and Robert Ward"
date: "15 JUN 2020"
output: bookdown::gitbook
# output:
#   bookdown::html_book:
#     theme: united
site: bookdown::bookdown_site
always_allow_html: yes
documentclass: memoir
classoption: oneside
# geometry: margin=.75in
---

```{r setup, include=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Class Introduction

## Topics & Class Structure

1. Git/GitHub setup and repository download (~45 minutes; interactive)
2. Ten-minute break
3. Using R for modeling with differential equations (~30 minutes; interactive)
4. Collaboration using Git (as time allows; instructor demonstration)

## Software Prerequisites

1. R 3.6.x or newer
2. RStudio 1.2.x or newer
3. Git 
4. Git Bash (included with Git for Windows) or another command-line application of your choice capable of using Git

## Human Prerequisites

We assume you have:

1. Working knowledge of R and RStudio;
2. Some experience with contemporary tidy coding concepts;
3. A need to work collaboratively on projects;
4. A healthy appreciation of dad jokes.

Try to follow along, at least through the differential equation section. It's okay to struggle to keep up with certain parts of this - we'll do our best to help you, but we also won't be offended if you decide to leave.

## Distance Learning Challenges

1. Don't be afraid to ask questions - both verbally and in chat.
2. If you miss something we said, it's likely others have too - you'll be helping them by speaking up.
3. Its difficult the know the speed of the class, so please communicate!

## Endstate

1. You have git configured on your computer;
2. You have linked git to github;
3. You have a repo cloned to your computer;
4. You can push, pull, and merge git conflicts in the repository;
5. You've learned the basics of using differential equations in R.

## Instructors Introduction

### MAJ Dusty Turner

Army 

- Combat Engineer
- Platoon Leader / XO / Company Commander
- Geospatial / Sapper / Route Clearance
- Hawaii / White Sands Missile Range / Iraq / Afghanistan

Education

- West Point '07
  - Operations Research, BS
- Missouri University of Science and Technology '12
  - Engineering Management, MS
- THE Ohio State '16
  - Integrated Systems Engineering, MS
  - Applied Statistics, Graduate Minor

Data Science

- R User Since '14
- Catch me on Twitter [`@dtdusty`](http://www.twitter.com/dtdusty)
- <http://dusty-turner.netlify.com/>

### Robert Ward

Education

- University of Chicago, '13
  - Political Science & English, BA
- Columbia University School of International and Public Affairs, '18
  - Master of International Affairs, Specialization in Advanced Policy and Economic Analysis
  
Data Science

- R user since 2011; also know some python and forgot some Stata
- Worked for GAO Applied Research & Methods
- ORSA at CAA and Army Leader Dashboard/Vantage PM team


## Lets Get Started...

### Prerequisite Packages

```{r eval=FALSE, include=TRUE}
install.packages(
  "tidyverse"
  dependencies = TRUE
  )
```

