---
title: "Intermediate R"
author: "MAJ Dusty Turner and Robert Ward"
date: "15 JUN 2020"
output: bookdown::gitbook
# output:
#   bookdown::html_book:
#     theme: united
site: bookdown::bookdown_site
always_allow_html: yes
documentclass: memoir
classoption: oneside
# geometry: margin=.75in
---

```{r setup, include=FALSE, cache = TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Class Introduction

Topics

1. R Project Set Up
2. git and hosting a git repository
3. Introductory git commands
4. Sharing a project via git
5. *Bonus* Differential Equations in R

## Expectations

By attending this tutorial, we assume you have...

1. working knowledge of R and RStudio
2. conteporary tidy coding concepts
3. a need to work collaborativly on a project
4. a healthy appreciation of Dad Jokes

Give it a shot, if its too much or too little, will not be offended if you leave.

Its okay to struggle.

## Prerequisites

1. R 3.6.x or newer
2. RStudio 1.2.x or newer
3. Git 
4. Git Bash (included with Git for Windows) or another command-line application of your choice capable of using Git


## Distance Learning Challenges

1. Don't be afraid to ask questions - both verbally and in chat
2. If you miss something we said, its likely others have too
3. Its difficult the know the speed of the class so please communicate!

## Class Structure

1. 2 hours of instruction
2. 1 ten minute break
3. We will ask for feedback to get a feel for understanding 

## Learning Recommendations

1. Use RMD files provided in repo (will get this this later)
2. Take notes with comments
3. Execute code along with us
4. Ask questions in chat

## Endstate

1. You have git configured on your computer
2. You have linked git to github or gitlab
3. You have a repo cloned to your computer.
4. You can push, pull, and merge git conflicts, on the repository.
5. You've learned a little more about differential equations in R.


## Instructors Introduction

### MAJ Dusty Turner

Army 

- Combat Engineer
- Platoon Leader / XO / Company Commander
- Geospatial / Sapper / Route Clearance
- Hawaii / White Sands Missile Range / Iraq / Afghanistan

Education

- West Point '07
  - Operations Research, BS
- Missouri University of Science and Technology '12
  - Engineering Management, MS
- THE Ohio State '16
  - Integrated Systems Engineering, MS
  - Applied Statistics, Graduate Minor

Data Science

- R User Since '14
- Catch me on Twitter [`@dtdusty`](http://www.twitter.com/dtdusty)
- <http://dusty-turner.netlify.com/>

### Robert Ward

Education

- University of Chicago, '13
  - Political Science & English, BA
- Columbia University School of International and Public Affairs, '18
  - Master of International Affairs, Specialization in Advanced Policy and Economic Analysis
  
Data Science

- R user since 2011; also know some python and forgot some Stata
- Worked for GAO Applied Research & Methods
- ORSA at CAA and Army Leader Dashboard/Vantage PM team


## Lets Get Started...

### Prerequisite Packages

```{r eval=FALSE, include=TRUE}
install.packages(
  "tidyverse"
  dependencies = TRUE
  )
```

